Using Sweat Na and Cl to Predict CFTR-RD and CRMS

### 2024-03-25 Edith Zemanick/Sweat Test/sweat_test_cf_conference.qmd
cf research conference done

---
title: "Using Sweat Na and Cl to Predict CFTR-RD and CRMS"
author: "Tim Vigers"
date: "today"
date-format: long
format: revealjs
editor: source
bibliography: Presentation.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association-10th-edition.csl
---

@@

The points with arrows to our dividing line are the *support vectors*.

@@

>>>>

---
title: "Using Sweat Na and Cl to Predict CFTR-RD and CRMS"
author: "Tim Vigers"
date: "today"
date-format: long
format: revealjs
embed-resources: true
editor: source
bibliography: Presentation.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association-10th-edition.csl
---

@@

@@

![](svm.png)
